\documentclass{article}
\usepackage{amsmath}

\begin{document}

\begin{center}
    \textbf{Jagannath University} \\
    Department of Computer Science and Engineering \\
    \textbf{2\textsuperscript{nd} Midterm Examination} \\
    Course Title: Computer Networks \hspace{0.2cm} Course Code: CSE-3107 \\
    Total Marks: 10 \hspace{0.2cm} Time: 30 Minutes
\end{center}

\noindent Answer the following Questions:

\begin{enumerate}
    \item Consider a datagram network using 8-bit host addresses. Suppose a router uses longest prefix match and has the following forwarding table:
    
    \[
    \begin{array}{|c|c|}
    \hline
    \textbf{Prefix Match} & \textbf{Interface} \\
    \hline
    1 & 0 \\
    11 & 1 \\
    111 & 2 \\
    \text{Otherwise} & 3 \\
    \hline
    \end{array}
    \]
    For each of the four interfaces, give the associated range of destination host address and the number of addresses in the range. \hspace{1cm} \textbf{(3 Marks)}
    
    \item An address in a block is given as 205.12.10.45. Find the number of addresses in the block, the first address, and the last address. \hspace{1cm} \textbf{(2 Marks)}
    
    \item What is the subnetwork address if the destination address is 150.45.34.56 and the subnet mask is 255.255.240.0? \hspace{1cm} \textbf{(2 Marks)}
    
    \item An organization is granted a block 208.28.190.0/24. The administrator wants to create 30 subnets.
    \begin{enumerate}
        \item Find the subnet mask. \hspace{1cm} \textbf{(3 Marks)}
        \item Find the number of addresses in each subnet. \hspace{1cm} \textbf{(3 Marks)}
        \item Find the first and last address in the first subnet. \hspace{1cm} \textbf{(3 Marks)}
        \item Find the first and last address in the last subnet (subnet 30). \hspace{1cm} \textbf{(3 Marks)}
    \end{enumerate}
\end{enumerate}

\end{document}
